---
title: "PSTAT274 Lab 01"
author: "AO XU"
date: "2022-10-03"
output: html_document
---


Q1
```{r}
set.seed(100)
x = runif(1000,-1,1)
y = x^2
cor(x,y)
cov(x,y)
```
X and y are uncorrelated since cor(x,y) = 0.06219732 which is very close to zero.

X and Y are not dependent since cov(x,y) is not equal to 0. 

It could happen that two variables are uncorrelated but not dependent.

Q2
```{r}
set.seed(1011)
x1 = runif(10,-1,1)
x2 = runif(100,-1,1)
x3 = runif(1000,-1,1)
mean(x1)
mean(x2)
mean(x3)
```
As sample size increases, sample mean is approaching to the true mean.

Q3
```{r}
n =100
rows = 1000
sim = matrix(runif(n*rows,-1,1),rows)
sample.mean = rowMeans(sim)
hist(sample.mean)
```
mean = 0, variance = 1/300 by using central limit theorem, it's normal distribution

Q4 
```{r}
uspop = scan("uspop.txt")
uspop
plot(uspop/1000000, type = "o", main = "US population", xlab = "Year", ylab = "Population", lwd = 2)
plot(sqrt(uspop/1000000), type = "o", main = "US population", xlab = "Year", ylab = "Population", lwd = 2)
```
For the sqrt, the graph is more linear。